% exp.tex
\section{Experience}
\cventry{March 2025 -- Present}{Tutor, Machine Learning}{School of Computing, Australian National University}{}{\textit{Supervisor: Dr.\ Rahul Shome, Yun Keun Chen, Thang Bui}}{%
\begin{itemize}[itemsep=0em]
  \item Teaching basic mathematical tools for machine learning and optimization.
  \item Introducing core deep learning systems, including CNNs and Transformer-based architectures.
  \item Marking papers in Statistical Machine Learning (Bayesian Inference).
\end{itemize}}

\cventry{March 2025 -- Present}{Head Tutor, Cybernetics}{School of Cybernetics, Australian National University}{}{\textit{Supervisor: Dr.\ Safiya Okai-Ugbaje}}{%
\begin{itemize}[itemsep=0em]
  \item Leading hands-on laboratory sessions for postgraduate coursework students.
  \item Assisting in the design and delivery of projects involving microprocessors, robotics, and machine learning.
  \item Teaching foundational programming concepts using Python.
\end{itemize}}

\cventry{Nov 2024 -- Feb 2025}{Quantitative Research Intern, Execution Speed and Success}{Optiver APAC, Sydney}{}{}{%
\begin{itemize}[itemsep=0em]
  \item Developed, implemented \& back-tested a statistical arbitration model on the Hong Kong exchange.
  \item Performed statistical analyses on large-scale financial data to uncover market patterns and operational inefficiencies in Korean market.
  \item Collaborated with traders and developers to build a proprietary, real-time Machine Learning decision-making system to build a system with 94\% accuracy.
\end{itemize}}

\cventry{Sep 2023 -- Sep 2024}{Graduate Research Assistant --- Fintech \& AI}{Research School of Management, Australian National University}{}{\textit{Principal Investigator: Dr. Priya Muthukannan}}{%
\begin{itemize}[itemsep=0em]
  \item Conducted qualitative analyses of open banking regimes using dynamic capabilities frameworks.
  \item Delivered introductory courses in data analysis for Business Information Systems.
  \item Developed innovative frameworks to assess the impact of AI on banking responses to technological shifts.
\end{itemize}}

\cventry{Jul 2022 -- Sep 2023}{Casual Sessional Academic --- Engineering}{School of Engineering, Australian National University}{}{\textit{Employers: Prof. Ian Petersen \& Prof. Iman Shames}}{%
\begin{itemize}[itemsep=0em]
  \item Tutored laboratory sessions for Advanced Control Systems (ENGN8824) for a cohort of 12 master’s students.
  \item Facilitated interactive problem-solving sessions for 34 students in Network Optimization and Control (ENGN4628).
  \item Led focused tutoring sessions for 16 students in Power Systems and Electronics (ENGN4625).
\end{itemize}}

\cventry{Mar 2022 -- Jun 2022}{Undergraduate Researcher --- Foundational Deep Learning}{School of Computing, Australian National University}{}{\textit{Supervisor: Prof. Richard Hartley, FAA}}{%
\begin{itemize}[itemsep=0em]
  \item Applied neural networks to assess the invertibility of differentiable functions in non-linear processes, achieving a 72\% RMSE hit rate using positional encoding.
  \item Demonstrated the limitations of normalizing flow networks for global invertibility, underscoring neural networks’ limitations as local approximators for smooth functions.
  \item Developed an FPGA-based TIMER algorithm to quantify the computational effort required for minimum convergence, accounting for floating-point precision constraints.
\end{itemize}}

\cventry{Dec 2021 -- Mar 2022}{Undergraduate Researcher --- Control \& Optimisation}{Research School of Engineering, Australian National University}{}{\textit{Supervisor: Prof. Ian Petersen, FAA}}{%
\begin{itemize}
  \item Developed a deterministic algorithm that outperformed classical Nesterov-like methods for convex functions.
  \item Applied control theory to design universal Lyapunov-based methods for predicting convergence rates in high-resolution ODE models.
\end{itemize}}

\cventry{Mar -- Aug 2021}{Head Automation Intern --- Power Systems Automation}{Calcutta Electric Supply Corporation, India}{}{\textit{Supervisor: Mr. Arindam Sanyal, Director}}{%
\begin{itemize}[itemsep=0em]
  \item Led a cross-functional team of 17 (including 5 interns and 12 field workers) to design and implement a self-healing mechanism for the Ring Main Unit-based power system at Chitpur Hospital Substation during the second COVID-19 wave in India.
\end{itemize}}

\cventry{Dec 2020 -- Mar 2021}{ML Research Intern --- Financial NLP}{Decimal Point Analytics, India}{}{\textit{Supervisor: Mr. Paresh Sharma, MD}}{%
\begin{itemize}[itemsep=0em]
  \item Engineered and optimized a financial metadata database for a RoBERTa-based question-answering system.
  \item Conducted client meetings for product reassessment and quality assurance, collaborating with diverse stakeholders.
\end{itemize}}

% \cventry{Sep -- Nov 2020}{Research Intern}{Laxmi Vilas Bank, India}{}{\textit{Supervisor: Mr. Parthasarathi Mukherjee, Ex-CEO}}{%
% \begin{itemize}
%   \item Devised a portfolio optimization method using competitive neural networks to analyze multiple time series datasets in real-time.
% \end{itemize}}

\cventry{May -- Aug 2020}{Summer Research Trainee --- Passive Radar Signal Processing}{Armament Research and Development Establishment, DRDO, India}{}{}{%
\begin{itemize}[itemsep=0em]
  \item Developed a Kalman filter–based technique to rapidly select optimal matched filters for incoming radar signals.
  \item Implemented an FPGA-based multi-processor interface for real-time analysis of long-range, noise-affected radar signals.
\end{itemize}}
